---
title: "Taro Mieno"
format:
  html:
    toc: true
  # typst: default
---

```{r}
#| include: false
library(dplyr)
library(data.table)
library(flextable)
library(officer)
```

::: {.columns}

::: {.column width="50%"}
Agricultural Economics\
University of Nebraska-Lincoln\
Filley Hall\
Lincoln, NE 68516
:::
<!--end of the 1st column-->
::: {.column width="50%"}
[Email: tmieno2@unl.edu](mailto: tmieno2@unl.edu)\
[Website](https://tmieno2.github.io/my-website/)
:::
<!--end of the 2nd column-->
:::
<!--end of the columns-->

### Professional Experience

Associate Professor, University of Nebraska-Lincoln (2021 - present)\
Assistant Professor, University of Nebraska-Lincoln (2015-2021)\
Postdoctoral Fellow, Luc Hoffmann Institute (2014--2015)\
Postdoctoral Research Associate, University of Minnesota (2014--2015)

---

### Education

**Ph.D., Agricultural and Applied Economics**, University of Illinois at Urbana-Champaign (2014)\
**M.S., Agricultural Economics**, University of Illinois at Urbana-Champaign (2009)\
**B.S., Forestry**, Hokkaido University (2007)

---

### Research Fields

Environmental and Resource Economics\
Applied Econometrics\
Precision Agriculture\
Agricultural Economics\
Production Economics

---

### Journal Articles (Peer-reviewed )

```{r}
#| output: asis
#| echo: false
#|
mybib <- RefManageR::ReadBib("data/publications.bib")

RefManageR::BibOptions(sorting = "ydnt")

mybib
```

---

### Other Publications

```{r}
#| output: asis
#| echo: false
other_pub_data <-
  jsonlite::fromJSON("data/other_publications.json") %>%
  # jsonlite::fromJSON("CV/other_publications.json") %>%
  data.table() %>%
  .[, other_pub_txt := paste0(item, ", ", media)]

categories <- unique(other_pub_data$category)

for (i in categories) {
  w_data <- other_pub_data[category == i, ]
  cat(paste0("**", i, "**\\\n\n"))
  cat(w_data[, paste0("- ", other_pub_txt)] %>% paste0(collapse = "\\\n"))
  cat("\n\n")
}

# paste0(collapse = "\\\n")
# cat()
```


---

### Teaching

```{r}
#| output: asis
#| echo: false
teaching_data <-
  jsonlite::fromJSON("data/teaching_experience.json") %>%
  # jsonlite::fromJSON("CV/teaching_experience.json") %>%
  data.table() %>%
  .[, course_txt := paste0(role, ": ", course, " ", semester)]

categories <- unique(teaching_data$category)

for (i in categories) {
  w_data <- teaching_data[category == i, ]
  cat(paste0("**", i, "**\\\n\n"))
  cat(w_data[, paste0("- ", course_txt)] %>% paste0(collapse = "\\\n"))
  cat("\n\n")
}

# paste0(collapse = "\\\n")
# cat()
```

---

### Presentations

```{r}
#| output: asis
#| echo: false
jsonlite::fromJSON("data/presentations.json") %>%
  # jsonlite::fromJSON("CV/data/referee_journals.json") %>%
  data.table() %>%
  .[, paste0('+ \"', title, '\" at **', conf_name, "** (", year, ")")] %>%
  paste0(collapse = "\\\n") %>%
  cat()
```


---

### Invited Talks

```{r}
#| output: asis
#| echo: false
jsonlite::fromJSON("data/invited_talks.json") %>%
  # jsonlite::fromJSON("CV/invited_talks.json") %>%
  data.table() %>%
  .[, paste0('- \"', title, '\" at **', inst, "** (", year, ")")] %>%
  paste0(collapse = "\\\n") %>%
  cat()
```

---

### External Grants

```{r}
#| output: asis
#| echo: false
jsonlite::fromJSON("data/external_grants.json") %>%
  # jsonlite::fromJSON("CV/external_grants.json") %>%
  data.table() %>%
  .[, paste0('- \"', title, '\", **', funder, "**, ", role, ", ", period, ", ", amount)] %>%
  paste0(collapse = "\\\n") %>%
  cat()
```

---

### Awards and Fellowships

```{r}
#| output: asis
#| echo: false
af_data <-
  jsonlite::fromJSON("data/awards_fellowship.json") %>%
  # jsonlite::fromJSON("CV/awards_fellowship.json") %>%
  data.table()

(
  af_list <-
    af_data %>%
    .[, paste0("- **", title, "**, ", inst, " (", year, ")")] %>%
    paste0(collapse = "\\\n") %>%
    cat()
)

```

---

### Referee Services

```{r}
#| include: false
referee_service_data <-
  jsonlite::fromJSON("data/referee_services.json") %>%
  # jsonlite::fromJSON("CV/data/referee_journals.json") %>%
  data.table()
```

**Journals**

```{r}
#| output: asis
#| echo: false
referee_service_data %>%
  dplyr::filter(category == "journal") %>%
  .[, .(year_num_list = paste0(year, "(", num, ")", collapse = ", ")), by = name] %>%
  .[, paste0("+ **", name, "**: ", year_num_list)] %>%
  paste0(collapse = "\\\n") %>%
  cat()
```


**Grant/Program**

```{r}
#| output: asis
#| echo: false
referee_service_data %>%
  dplyr::filter(category == "grant") %>%
  .[, paste0("+ ", name, ": ", year)] %>%
  paste0(collapse = "\\\n") %>%
  cat()
```

**Conference Abstract**

```{r}
#| output: asis
#| echo: false
referee_service_data %>%
  dplyr::filter(category == "conf-abstract") %>%
  .[, paste0("+ ", name, ": ", year)] %>%
  paste0(collapse = "\\\n") %>%
  cat()
```


---

### Professional Services

```{r}
#| include: false
professional_service_data <-
  jsonlite::fromJSON("data/professional_services.json") %>%
  # jsonlite::fromJSON("CV/data/referee_journals.json") %>%
  data.table()
```

**Editorship**

```{r}
#| output: asis
#| echo: false
professional_service_data %>%
  dplyr::filter(category == "editor") %>%
  .[, paste0("+ ", name, ": ", year)] %>%
  paste0(collapse = "\\\n") %>%
  cat()
```

**University of Nebraska-Lincoln**

```{r}
#| output: asis
#| echo: false
professional_service_data %>%
  dplyr::filter(category == "unl") %>%
  .[, paste0("+ ", name, ": ", year)] %>%
  paste0(collapse = "\\\n") %>%
  cat()
```

---

### Mentorship (Graduate Students/Postdocs)

```{r}
#| include: false
students_service_data <-
  jsonlite::fromJSON("data/students.json") %>%
  # jsonlite::fromJSON("CV/data/referee_journals.json") %>%
  data.table() %>%
  .[, type := factor(type, levels = c("Ph.D.", "MSc", "Postdoc"))] %>%
  .[order(type, year_grad), ]

num_lines <- nrow(students_service_data)
```

```{r}
#| echo: false
flextable::flextable(students_service_data) %>%
  flextable::set_header_labels(
    values = list(
      name = "Name",
      inst = "Institution",
      year_grad = "Year of \n Graduation",
      role = "My role",
      type = "Degree",
      job = "Immediate \nPlacement"
    )
  ) %>%
  flextable::autofit() %>%
  hline(
    i = 1:(num_lines - 1),
    border = fp_border(
      color = "grey",
      width = 1
    )
  ) %>%
  footnote(
    i = 1,
    j = 2,
    part = "header",
    value = as_paragraph("UNL: University of Nebraska-Lincoln, UIUC: University of Illinois at Urbana-Champaign"),
    ref_symbols = "++"
  )
```